SpikeIn MSstatsPTM Analysis

### 2022-06-15 code/MSstatsPTM_Simulation_Analysis.Rmd
addressed some comments

## Label Models
adj_results$Model <- "Proposed"
no_adj_results$Model <- "Proposed no adjustment"
ttest_results$Model <- "T-Test no adjustment"
ttest_adj_results$Model <- "T-Test"
limma_model_results$Model <- "Limma no adjustment"
limma_adj_model_results$Model <- "Limma"

@@

cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999")
cbPalette_first <- c("#E69F00", "#F0E442", "#56B4E9", "#0072B2", "#009E73", "#D55E00", "#CC79A7", "#999999")
```

@@

png("../main/images/sim1_FDR_all_models.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no adjustment", "Limma", 
                                               "Limma no adjustment", "T-Test", "T-Test no adjustment")),
                  ) %>%
  filter(conditions == 4 & sd == .3 & rep == 5) %>% 
  ggplot() + geom_col(aes(x = Model, y = fpr, fill = Model)) + #, size = Replicates
  scale_colour_manual(values=cbPalette_first) +
  # scale_size_manual(values = c(3,5,7,9)) +
  # facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  ylim(0.0, 0.4) + 
  theme(axis.text.x = element_text(angle = 45, hjust=1, vjust = 1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=16),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 1: FDR all models", x = "Model", y = "FDR") + 
     guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("../supplementary/sim_new/sim3_Accuracy.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed_no_adj", "limma_no_adj", 
                                               "Limma", "ttest_no_adj", "T-Test")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = accuracy, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  scale_size_manual(values = c(3,5,7,9)) + 
  facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 2: Accuracy adjusted models", x = "Model", y = "Accuracy") + 
   guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))
dev.off()
```

>>>>

## Label Models
adj_results$Model <- "Proposed"
adj_results$Color_Model <- "Proposed"
adj_results$Adj = TRUE
no_adj_results$Model <- "Proposed no adjustment"
no_adj_results$Color_Model <- "Proposed"
no_adj_results$Adj = FALSE
ttest_results$Model <- "T-Test no adjustment"
ttest_results$Color_Model <- "T-Test"
ttest_results$Adj = FALSE
ttest_adj_results$Model <- "T-Test"
ttest_adj_results$Color_Model <- "T-Test"
ttest_adj_results$Adj = TRUE
limma_model_results$Model <- "Limma no adjustment"
limma_model_results$Color_Model <- "Limma"
limma_model_results$Adj = FALSE
limma_adj_model_results$Model <- "Limma"
limma_adj_model_results$Color_Model <- "Limma"
limma_adj_model_results$Adj = TRUE

@@

cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999")
cbPalette_first <- c("#56B4E9", "#E69F00", "#009E73", "#56B4E9", "#009E73", "#009E73", "#CC79A7", "#999999")
```

@@

png("../main/images/sim1_FDR_all_models.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no adjustment", "Limma", 
                                               "Limma no adjustment", "T-Test", "T-Test no adjustment")),
                  ) %>%
  filter(conditions == 4 & sd == .3 & rep == 5) %>% 
  ggplot() + geom_col(aes(x = Model, y = fpr, fill = Color_Model, alpha = Adj)) + #, size = Replicates
  scale_fill_manual(values=cbPalette_first) +
  scale_alpha_manual(values = c(.5, 1.0)) + 
  # scale_size_manual(values = c(3,5,7,9)) +
  # facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  ylim(0.0, 0.4) + 
  guides(alpha = "none") + 
  guides(fill = "none") + 
  theme(axis.text.x = element_text(angle = 45, hjust=1, vjust = 1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=16),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 1: False Discovery Rate by Model", x = "Model", y = "FDR") + 
     guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("../main/images/sim3_Accuracy.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed_no_adj", "limma_no_adj", 
                                               "Limma", "ttest_no_adj", "T-Test")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = accuracy, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  scale_size_manual(values = c(3,5,7,9)) + 
  facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 2: Model Accuracy", x = "Model", y = "Accuracy") + 
   guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))
dev.off()
```

### 2022-06-15 code/Spike-in_Analysis.Rmd
Added data availability info
addressed some comments

---
title: "Spike-in_MSstatsPTM_Analysis"
author: "Devon Kohler"
date: "6/18/2021"
output: html_document
---

@@

>>>>

---
title: "SpikeIn MSstatsPTM Analysis"
author: "Devon Kohler"
date: "3/7/2022"
output: html_document
---

@@

summary_df$PTM$ProcessedData
summary_df$PTM$ProcessedData$global_prot = sapply(summary_df$PTM$ProcessedData$PROTEIN, function(x){str_split(x, "_")[[1]][1]})

summary_df$PTM$ProcessedData$global_prot %>% n_distinct()
summary_df$PTM$ProcessedData$PROTEIN %>% n_distinct()
summary_df$PTM$ProcessedData$FEATURE %>% n_distinct()

summary_df$PROTEIN$ProcessedData$PROTEIN %>% n_distinct()
summary_df$PROTEIN$ProcessedData$PEPTIDE %>% n_distinct()
